\chapter{State of the Art}
In this chapter I will write about the literature study that has been carried out. Things to include in this chapter is: Lane detection in general, Image processing- hough transform etc.. MCS. Misra-c? Information about the board  (EMC2 and zedboard)

\section{Lane keeping}
For a human driving may seem like a simple process where two basic tasks are involved. The first is to keep the vehicle and the road and the second to avoid collisions. But in reality driving is not so trivival, a driver need to continoulsly analyze the road scene and choose and execute the appropriate maneuvers to deal with the current situation. To help the drivers do these tasks Driving Assistance Systems (DAS) have been developed. These systems can help the driver to percieve the blind area in the road for an example. An extension is the Advanced Driving Assistance System (ADAS) Which can perform basic tasks like: Lane following, Lane keeping assistance, Lane departure warning, lateral control, intelligent cruise control, collision warning and ultimately autonomous driving.\\

The main bottleneck in the development of ADAS systems is the perception problem, which has two elements: road and lane perception, and obstacle detection. In this section I will investigate the first element and study what the current state of the art is.\\

Today there are several different sensing modalities used for lane detection. Some examples are monocular vision, stereo vision, LIDAR, IMU data, GPS.\\


Vison is the most prominent research area due to the fact that road signs/markings are made for human vision. Vision sensors provides good position estimation on the road without the need for any other modalieties. However, there are situations when vision sensors simply cannot perform well, for example in extreme weather conditions or when in driving off-road conditions. In this kind of situations it is possible to use sensor fusion with other sensor modalities to provide better position estimate, and it is the reason why LIDAR and GPS are important compliments to vision for reaching full autonomous driving.\\




In its basic setting the lane detection problem seems like a simple one. The only thing needed is to detect a host lane and only for a short distance ahead. A simple Hough transform-based algorithm solves the problem in 90\% of highway cases %\citep{•}. 
But the impression that the problem is easy is misleading and building a useful system requires a huge R\& D effort. One of the reasons is the high reliability demands. In order to be useful the system needs to reach very low error rates. The exact amount of false alarms is still a subject of research %\citep{•}.
At 15 frames per second, 1 false alarm per hour means only one error in 54,000 frames. \\


One factor that makes ADAS hard to implement on large scale is the large amount of different conditions that has to be taken care of. The main sources for condition diversity are:\\
-Lane and road appearance\\
-image clarity issues\\
-poor visibility conditions\\

\section{Modalities}
In this section the modalities used for road and lane detection will be described more in detail.

\subsection{Monocular vision}
The monocular vision system is frequently used for road and lane detection. It is more simply put one camera mounted on the vehicle. The recuired resolution can be derived from FORMEL (Bar hillel).\\
When humans drive we continously look at the road boundries, the lane markings and the road texture among other things. These road boundries are designed so that they should be visible for human drivers in all driving condition. Self driving vehicles that are supposed to share the road with human drivers will therefore most likely have to rely on the same perceptual cues as humans. 
\subsection{LIDAR}
Light detection and ranging (LIDAR) is a modalitiy that have been used to a large extent in the development of autonomous vehicles for research purposes. The LIDAR measures the environment around the vehicle in 3D. The LIDAR sends out light pulse and measures the time for it to come back. As it is an active light source it is not dependent of having good natural lighting as with a regular camera. \\

LIDAR sensors can perform well in certain situations for example in rural areas to detect road boundries (Lakshmanan) but are not well suited for multilane roads without vision data. As the LIDAR only measures 3D structures it not able to detect road markings, although some research have been done on intensity measurement with LIDAR (Källa Bar Hillel) which would make it possible to detect line markings. One huge drawback with this modality is that the sensors are still very expensive and thus not yet an alternative for implementation in regular passenger vehicles.
\subsection{Stereo imaging}
Stereo imaging is the use of two cameras instead of one camera in order to obtain 3D information about the surronding. It is a step in between the monocular vision and the LIDAR as it is much cheaper to implement than LIDAR but generally performs less good in terms of accuracy and reliability.  Also the stereo imaging system generally requires greater processing power 
          
\section{Use case}
My degree project will be about the perception problem for autonomous vehicles. The group is developing a vehicle platoon where one vehicle drives autonomously around a predefined track and a second vehicle is following the first. Use case number 3 in the safecop project description "Vehicle controll loss warning" ties well with my own project. In the safecop project description there is mentioned "The US National Highway Traffic Safety Administration (NHTSA) has estimated that “V2V safety
applications have the potential to address approximately 80\% of crashes for unimpaired drivers”." The idea is to implement obstacle detection on the road and send out a warning to other vehicles in the platoon or close surrounding.

With this use case in mind five requirements have been developed:\\
1. The system should be able to keep a constant speed v while keeping track of the road.\\
2. If any object is detected on the road, the vehicle platoon should do an emergency stop.\\
3. If the vehicle sends out a warning to other vehicles in the platoon, they should stop within the time limit of x s. \\
4. \\
5\\

